Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-17 manuscript/manuscript.Rmd
arxiv style, and add headers

abstract: |
  Existing methods for optimal control methods struggle to deal with the complexity commonly encountered in real-world systems, including dimensionality, process error, model bias and heterogeneity. 
  Instead of tackling these complexities directly, researchers have typically sought to find exact optimal solutions to simplified models of the processes in question. 
  When is the optimal solution to a very approximate, stylized model better than an approximate solution to a more accurate model? 
  This question has largely gone unanswered owing to the difficulty of finding even approximate solutions in the case of complex models.  
  Our approach draws on recent algorithmic and computational advances in deep reinforcement learning. 
  These methods have hitherto focused on problems in games or robotic mechanics, which operate under precisely known rules. 
  We demonstrate the ability for novel algorithms using deep neural networks to successfully approximate such solutions (the "policy function" or control rule) without knowing or ever attempting to infer a model for the process itself. 
  This powerful new technique lets us finally begin to answer the question.
  We show that in many but not all cases, the optimal policy for a carefully chosen over-simplified model can still out-perform these novel algorithms trained to find approximate solutions to simulations of a realistically complex system. 
  This illustrates the promise of combining complex, realistic simulations with emerging machine-learning techniques to improve our understanding and management of ecological systems.

bibliography: bibliography.bib
biblio-style: spphys

# bibstyle options spbasic(default), spphys, spmpsci
output: rticles::springer_article

@@

Despite the complexity inherent in natural ecosystems, analytically tractable models have long played an essential role in their understanding and management.
Ecological management may be understood as an optimal control problem - a manager must determine a sequence of actions (a "policy") to optimize some desired objective or combination of objectives (conservation goals, natural resource extraction, economic and social constraints.)

@@

We trained a DRL agent to obtain a candidate policy
\begin{align*}
  \pi: (X_t,Y_t,Z_t) \mapsto h_t
\end{align*}
for eq. \eqref{eq:3d model}.
The agent could fully and precisely observe the state of the system at each time step and decide on its harvest based on this information. 
The agent was trained using the PPO algorithm, using a neural network with two hidden layers of 64 neurons to express $\pi$.
Details of the training process may be found in App. \ref{app:tbd}.
Our code is available at TBD.

>>>>

abstract: |
  Write

bibliography: bibliography.bib
#biblio-style: spphys

header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{lineno}
  - \usepackage{setspace}
  - \usepackage{bookmark}
  - \linenumbers
  - \doublespacing

# bibstyle options spbasic(default), spphys, spmpsci
# output: rticles::springer_article

output: 
  rticles::arxiv_article:
    keep_tex: true

editor_options: 
  markdown: 
    wrap: sentence

@@

<!--
Existing methods for optimal control methods struggle to deal with the complexity commonly encountered in real-world systems, including dimensionality, process error, model bias and heterogeneity. 
Instead of tackling these complexities directly, researchers have typically sought to find exact optimal solutions to simplified models of the processes in question. 
When is the optimal solution to a very approximate, stylized model better than an approximate solution to a more accurate model? 
This question has largely gone unanswered owing to the difficulty of finding even approximate solutions in the case of complex models.  
Our approach draws on recent algorithmic and computational advances in deep reinforcement learning. 
These methods have hitherto focused on problems in games or robotic mechanics, which operate under precisely known rules. 
We demonstrate the ability for novel algorithms using deep neural networks to successfully approximate such solutions (the "policy function" or control rule) without knowing or ever attempting to infer a model for the process itself. 
This powerful new technique lets us finally begin to answer the question.
We show that in many but not all cases, the optimal policy for a carefully chosen over-simplified model can still out-perform these novel algorithms trained to find approximate solutions to simulations of a realistically complex system. 
This illustrates the promise of combining complex, realistic simulations with emerging machine-learning techniques to improve our understanding and management of ecological systems.
-->

Despite the complexity inherent in natural ecosystems, analytically tractable models have long played an essential role in their understanding and management.
Ecological management may be understood as an optimal control problem - a manager must determine a sequence of actions (a "policy") to optimize some desired objective(s) and constraints (e.g. conservation goals, natural resource extraction, economic and social constraints.)

@@

We trained a DRL agent to obtain a candidate policy
\begin{align*}
  \pi: (X_t,Y_t,Z_t) \mapsto h_t
\end{align*}
for eq. \eqref{eq:3d model}.
The agent could fully and precisely observe the state of the system at each time step and decide on its harvest based on this information.
